---
title: "wk9-homework-Hafer-Jocelyn"
author: "Jocelyn Hafer"
date: "November 23, 2015"
output: html_document
---

#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.

```{r}
is.a.number <- function(x) {
  if(is.na(x))
     print("Is NA") 
  else  
  if(class(x) !="numeric" & class(x) !="integer")
     print("I have no clue")
 else 
  print("Is a number")
}
```

#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}
prime <- function(x) {
  is.wholenumber <-
    function(x, tol = .Machine$double.eps^0.5)  abs(x - round(x)) < tol

  y <- (x/2)
  z <- (x/3)
  if(
    (is.wholenumber(x) == "FALSE"))
    print("Please enter an integer between 3 and 100")
  else 
    if((x<3) | (x>100))
    print("Please enter an integer between 3 and 100")
  else 
    if((is.wholenumber(y) == "TRUE") | (is.wholenumber(z) == "TRUE"))
    print("FALSE")
  else
    print("TRUE")
      }
```

#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
my_plot2 <- function(variable, label, title, theme, density) {
  
  if(theme == "bw")
    e <- theme_bw()
  else
    if(theme == "grey")
      e <- theme_grey()
    else
      if(theme == "classic")
        e <- theme_classic()
      else
        e <- theme_minimal()
      f <- geom_density()
      
      if(density == "TRUE")
        d <- qplot(variable, 
                   xlab = label) + 
          ggtitle(title) + e + f
      else
      d <- qplot(variable, 
                 xlab = label) + 
        ggtitle(title) + e
      
      print(d)
}
```

b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}
scatter <- function(x, y, title, smooth) {
  if(smooth == "TRUE")
    f <- geom_smooth()
  qplot(x,y) + ggtitle(title) + f
}
```

#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
